Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit

### 2023-06-16 Manuscript/Manuscript.Rmd
Update key resource table

## UV-avoidance circuits of extraocular photoreceptors

@@

```{r echo=FALSE}
library(readxl)
key_resource_table <- read_excel("key_resource_table/key_resource_table.xls")
df_key_resource_table <- as.data.frame(key_resource_table)
knitr::kable(df_key_resource_table, format = "html", booktabs = TRUE)
```

@@

\begin{align*}
\frac{d C_P(t)}{dt} &= 1 - \delta^{C_P} C_P(t) + K_{UV}^{C_P} UV(t) C_O(t)  + K_{G}^{C_P} G(t) , \\
\frac{dC_O(t)}{dt} &= 1 - \delta^{C_O} C_O(t) - K_{UV}^{C_O} UV(t) C_O(t), \\
\frac{dG(t)}{dt} &= 1 - \delta^{G} G(t) + K_{GC2}^G \left(1 - UV(t)\right) G(t) + K_{GC1}^G N(t) , \\
\frac{dS(t)}{dt} &= UV(t) - \frac{S(t)}{\tau_S}, \\
\frac{dC_N(t)}{dt} &= 1 - \delta^{C_N} C_N(t) + K_{S}^{C_N} S(t), \\
\frac{dN(t)}{dt} &= 1 - \delta^{N} N(t) + K_{C_N}^{N} C_N(t), \\
\frac{dC_R(t)}{dt} &= 1 - \delta^{C_R} C_R(t) - K_{S}^{C_R} S(t) + K_{C_P}^{C_R} C_P(t) - K_{C_N}^{C_R} C_N(t) C_R(t), \\
UV(t) &=
    \begin{cases}
        a, & t_{UV\: start} \leq t \leq t_{UV\: end}\\
        0, & \text{otherwise}
    \end{cases}   .
\end{align*}

## Data analysis and figure preparation

>>>>

**UV-avoidance circuits of extraocular photoreceptors**

@@

```{r echo=FALSE, warning=FALSE}
library(readxl)
key_resource_table <- read_excel("key_resource_table/key_resource_table.xls")
df_key_resource_table <- as.data.frame(key_resource_table)
df_key_resource_table <- replace(df_key_resource_table, is.na(df_key_resource_table), "")
knitr::kable(df_key_resource_table, format = "html", booktabs = TRUE)

@@

```{=tex}
\begin{align*}
\frac{d C_P(t)}{dt} &= 1 - \delta^{C_P} C_P(t) + K_{UV}^{C_P} UV(t) C_O(t)  + K_{G}^{C_P} G(t) , \\
\frac{dC_O(t)}{dt} &= 1 - \delta^{C_O} C_O(t) - K_{UV}^{C_O} UV(t) C_O(t), \\
\frac{dG(t)}{dt} &= 1 - \delta^{G} G(t) + K_{GC2}^G \left(1 - UV(t)\right) G(t) + K_{GC1}^G N(t) , \\
\frac{dS(t)}{dt} &= UV(t) - \frac{S(t)}{\tau_S}, \\
\frac{dC_N(t)}{dt} &= 1 - \delta^{C_N} C_N(t) + K_{S}^{C_N} S(t), \\
\frac{dN(t)}{dt} &= 1 - \delta^{N} N(t) + K_{C_N}^{N} C_N(t), \\
\frac{dC_R(t)}{dt} &= 1 - \delta^{C_R} C_R(t) - K_{S}^{C_R} S(t) + K_{C_P}^{C_R} C_P(t) - K_{C_N}^{C_R} C_N(t) C_R(t), \\
UV(t) &=
    \begin{cases}
        a, & t_{UV\: start} \leq t \leq t_{UV\: end}\\
        0, & \text{otherwise}
    \end{cases}   .
\end{align*}
```
## Data analysis and figure preparation
